Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-19 sections/model.tex
Merged ice dynamics and bed interface

\subsection{Ice dynamics}

@@

@@

\subsection{Glacier bed interface}

The glacier bed topography response to the ice load is computed by a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}\todo{check ref.}. To compute basal temperatures with higher accuracy, the thermal model is extended 1\,km into the bedrock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as basal condition to this model.

>>>>

\subsection{Ice thermodynamics}

@@

SIA and SSA velocities are computed by finite difference methods on a 10km-resolution horizontal grid of 300 by 150 points. SIA velocities follow temperature-dependant creep. Temperatures are derived from an enthalpy formulation \citep{aschwanden-etal-2012} and computed in three dimensions on 51 irregularly spaced layers in ice and 11 regularly spaced layers in rock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as lower boundary condition to the thermal model, and surface air temperature from the various climate forcing is used as upper boundary condition.

@@

The glacier bed topography responds to the ice load following a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}\todo{check ref.}.
